---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# inbreedR

![Build Status](https://travis-ci.org/mastoffel/inbreedR.svg?branch=master)

inbreedR provides functions and workflows for the analysis of inbreeding and heterozygosity-fitness correlations (HFCs) based on molecular markers such as microsatellites and SNPs. It has four main application areas:

* Quantify variance in inbreeding level through estimation of identitiy disequilibria (g2), 
  heterozygosity-heterozygosity correlations (HHC) and variance in standardized multilocus heterozygosity (sMLH)

* Calculate g2 for large SNP datasets through the use of a formula that avoids double summations and 
  has not been implemented in any software. The use of data.table and parallelization allow bootstrap
  and permutation tests with acceptable computation time
  
* Estimate important parameters such as the influence of inbreeding on heterozygosity and fitness

* Get insights on the sensitivity of these measures towards the number of genetic markers used in your
  study through re- and subsampling tests.

You can install:

* the latest released version from CRAN (not yet) with

    ```R
    install.packages("inbreedR")
    ```

* the latest development version from github with

    ```R
    if (packageVersion("devtools") < 1.6) {
      install.packages("devtools")
    }
    devtools::install_github("mastoffel/inbreedR", build_vignettes = TRUE)
    ```
   

If you encounter a clear bug or if you have any suggestions for improvement, just contact me: 
martin.adam.stoffel[at]gmail.com

## Get started with inbreedR

To get started read the vignette:  

```{r, eval = FALSE}
vignette("inbreedR_step_by_step", package = "inbreedR")
```


 
    



